### 2013-05-03 menger.tex
2-Markov doesn't imply Markov in Mneger game

  \begin{proof}
    First, suppose $X$ wasn't Menger. Then there would exist open covers $\mathcal{U}_0,\mathcal{U}_1,\dots$ of $X$ such that for any choice of finite subcollections $\mathcal{F}_n\subseteq\mathcal{U}_n$, $\bigcup_{n<\omega} \mathcal{F}_n$ isn't a cover of $X$. Thus $C\prewin\mengame{X} \Rightarrow S \not\win\mengame{X}$.

@@

  \begin{lemma}
    For all $\alpha_0, \alpha_1, \dots < \omega_1$ and functions $\tau:\omega_1\times\omega \rightarrow [\omega_1]^{<\omega}$, $\{\tau(\alpha_n,n): n<\omega\}$ is not a cover for $\{\beta:\forall n<\omega (\beta < \alpha_n)\}$.
  \end{lemma}

  \begin{proof}
    Let $P_n = \{\beta: \beta < \alpha \Rightarrow \beta \in \tau(\alpha, n)\}$. Observe that each $P_n$ is finite; else there is some $\alpha$ larger than every member of $P_n$ such that $P_n \subseteq \tau(\alpha, n)$.

@@

    Now, suppose that $\sigma(\mc{U}, n)$ was a winning Markov strategy and aim for a contradiction. Consider the covers \[\mc{U}(\alpha) = \{[\alpha,\omega_1)\cup\{\infty\}\} \cup \{\{\beta\}:\beta < \alpha\}\] and define $\tau(\alpha,n)$ to be the union of singletons chosen by $\sigma(\mathcal{U}(\alpha),n)$. As $\sigma$ was a winning strategy, for all $\alpha_0, \alpha_1, \dots < \omega_1$, $\{\sigma(\mathcal{U}(\alpha_n),n): n<\omega\}$ must cover $\oneptlind{\omega_1}$, and thus $\{\tau(\alpha_n,n): n<\omega\}$ must cover $\{\beta:\forall n<\omega (\beta < \alpha_n)\}$, contradiction.
  \end{proof}

>>>>

  \begin{proof}
    Result due to (???)

    First, suppose $X$ wasn't Menger. Then there would exist open covers $\mathcal{U}_0,\mathcal{U}_1,\dots$ of $X$ such that for any choice of finite subcollections $\mathcal{F}_n\subseteq\mathcal{U}_n$, $\bigcup_{n<\omega} \mathcal{F}_n$ isn't a cover of $X$. Thus $C\prewin\mengame{X} \Rightarrow S \not\win\mengame{X}$.

@@

  \begin{lemma}
    For all functions $\tau:\omega_1\times\omega \rightarrow [\omega_1]^{<\omega}$, there exists a sequence $\alpha_0, \alpha_1, \dots < \omega_1$ such that $\{\tau(\alpha_n,n): n<\omega\}$ is not a cover for $\{\beta:\forall n<\omega (\beta < \alpha_n)\}$.
  \end{lemma}

  \begin{proof}
    Let $P_n = \{\beta: \beta < \alpha \Rightarrow \beta \in \tau(\alpha, n)\}$. Observe that each $P_n$ is finite; else there is some $\alpha$ larger than every member of some countably infinite $P_n^*\subseteq P_n$ such that $P_n^* \subseteq \tau(\alpha, n)$.

@@

    Now, suppose that $\sigma(\mc{U}, n)$ was a winning Markov strategy and aim for a contradiction. Consider the covers \[\mc{U}(\alpha) = \{[\alpha,\omega_1)\cup\{\infty\}\} \cup \{\{\beta\}:\beta < \alpha\}\] and define $\tau(\alpha,n)$ to be the union of singletons chosen by $\sigma(\mathcal{U}(\alpha),n)$.

    Using the sequence $\alpha_0, \alpha_1,\dots<\omega_1$ from the previous lemma, we consider the play $\mc{U}(\alpha_0),\mc{U}(\alpha_1),\dots$.

    As $\sigma$ was a winning strategy, $\{\sigma(\mathcal{U}(\alpha_n),n): n<\omega\}$ must cover $\oneptlind{\omega_1}$, and thus $\{\tau(\alpha_n,n): n<\omega\}$ must cover $\{\beta:\forall n<\omega (\beta < \alpha_n)\}$, contradiction.
  \end{proof}

  We require a lemma.

  \begin{lemma}
    There exist injective functions $f_\alpha:\alpha\to\omega$ such that if $\alpha<\beta$, then \[f_\beta\rest\alpha =^* f_\alpha\] that is, $f_\beta\rest\alpha$ and $f_\alpha$ agree on all but finitely many ordinals.
  \end{lemma}

  \begin{example}
    $F \kmarkwin{2} \mengame{\oneptlind{\omega_1}}$
  \end{example}

  \begin{proof}
    Using the functions $f_\alpha$ from the previous lemma, let \[\tau(\alpha_n,\alpha_{n+1},n+1)=f_{\alpha_n}^{-1}([0,n]) \cup \{\beta<\alpha_n,\alpha_{n+1} : f_{\alpha_n}(\beta)\not=f_{\alpha_{n+1}}(\beta)\}\]

    For any sequence $\alpha_n$, suppose that $\beta<\alpha_n$ for all $n$, and $\beta$ is not covered by \[\{\tau(\alpha_n,\alpha_{n+1},n+1): n<\omega\}\] Then we see first that $f_{\alpha_n}(\beta)=f_{\alpha_{n+1}}(\beta)$ for all $n$. However, $f_{n}(\beta)>n$ for all $n$ as well, which is a contradiction.

    Finally, for each open cover $\mc{U}$, assign arbirtary $\alpha(\mc{U})$, $U(\mc{U})$ such that $[\alpha(\mc{U}),\omega_1)\cup\{\infty\}$ is a subset of $U(\mc{U})\in\mc{U}$. Then a $2$-Markov strategy $\sigma(\mc{U}_n,\mc{U}_{n+1},n+1)$ which chooses $U(\mc{U}_n)$ and covers the finite set $\tau(\alpha(\mc{U}_n),\alpha(\mc{U}_{n+1}),n+1)$ is a winning strategy for $F$.
  \end{proof}
